A matrix-free approach for finite-strain hyperelastic problems using geometric multigrid

### 2018-11-01 doc/large_strain.tex
make J_q and fix complexity of MF mass matrix

@@

        &\approx \sum_q \sum_j \tilde{a}(\gz N_i,\gz N_j)(\gz x_q) x_j w_q \\
        &= \sum_K \sum_q \sum_j \tilde{a}(\gz N_i,\gz N_j)(\gz \xi_q) x_j w_q J^K

@@

  y_{i} = y_{i_1\,i_2} & = J^K \sum_{q_1} \sum_{q_2} \sum_{j_1} \sum_{j_2}

@@

  \widetilde{w}_{q_1} \widetilde{w}_{q_2}

@@

  &= J^K

@@

@@

Since each of these $2\times d$ loops has a complexity of $n$ and we perform them for $n^d$ values in quadrature points or values in degrees of freedoms simultaneously, what results is an algorithm with arithmetic complexity of $\mathcal{O}(dn^{d+1})$.

>>>>

  \begin{split}

@@

        &\approx \sum_K \sum_q \sum_j \tilde{a}(\gz N_i,\gz N_j)(\gz \xi_q) x_j w_q J^K_q
  \end{split}

@@

  y_{i} = y_{i_1\,i_2} & = \sum_{q_1} \sum_{q_2} \sum_{j_1} \sum_{j_2}

@@

  \widetilde{w}_{q_1} \widetilde{w}_{q_2} J^K_{q1\,q2}

@@

  &=

@@

  J^K_{q1\,q2}

@@

Since each of these $2\times d$ loops has a complexity of $n$ and we perform them for $n^d$ values in quadrature points or values in degrees of freedoms simultaneously, what results is an algorithm with arithmetic complexity of $\mathcal{O}(2dn^{d+1})$.
